---
title: "index"
author: "D'Angelo Francis; Su Yeon Seo"
format: html
---
[Assignment 4](https://georgetown.instructure.com/courses/198228/assignments/1109024)

```{r setup, message=FALSE, warning=FALSE}

# make sure to load all packages here up top. If you need to install a package, include the commented code here as well :)

library(fontawesome) # install.packages("fontawesome") - for waffle graphs
library(styler) # install.packages("styler") - check for Tidy style guide adherence
library(lintr) # install.packages("lintr") - check for Tidy style guide adherence
library(tidyverse)
library(readxl)
library(haven)
library(tidyverse)
library(patchwork) # easy combine plots
library(tigris) # direct download of shape files from US Cenus 
library(sf) # manipulate shapefiles 
library(tidycensus) # shapefiles from Census 
library(rgeoboundaries) # international boundaries 
library(ggrepel)  # install.packages("ggrepel")
library(janitor)  # install.packages("janitor")
library(ggthemes) # install.packages("ggthemes")
library(crsuggest) # install.packages("crsuggest")


options(scipen=999) # no scientific notation for my plots


```

## Quick Reference Links:

I believe that we will need these links 

- [Figures](https://quarto.org/docs/authoring/figures.html)
- [Cross Reference](https://quarto.org/docs/authoring/cross-references.html)
- [Tidyverse Style Guide Packages](https://style.tidyverse.org/)
- [Urban Style Visualization Style Guide](https://urbaninstitute.github.io/r-at-urban/graphics-guide.html)

Research Question: What is the relationship between GRDP, household income, and women's rights on fertility among South Koreans by province? 

## Graph 1 - South Korean Fertility Rates by Province 

Note - Probably want to attach graph or 

```{r graph 1, message=FALSE, warning=false}

# getting geospatial data prepped

rok <- geoboundaries(
  country = "Republic of Korea",
  adm_lvl = "adm1")

rok_cities <- 
  read_sf("data/cities.geojson") |>
  clean_names() |>
  filter(ctry == "South Korea")

# bringing in fertility data source , cleaning data up

rok_fertility_province_2022 <- 
  read_csv("data/Agespecific_Fertility_Rate_Province__20241008012056.csv") |>
  clean_names() |>
  pivot_longer(
    cols = starts_with("x", ignore.case = TRUE),
    names_to = "year",
    values_to = "fertility_rate"
    ) |>
  rename(shapeName = by_province_1 , age = by_age_1) |>
  select(-by_variant_1) |>
  filter(shapeName != "Whole country", age == "TFR", year == "x2022") |>
  mutate(shapeName = case_when(
    shapeName == "Chungcheongbuk-do" ~ "North Chungcheong",
    shapeName == "Chungcheongnam-do" ~ "South Chungcheong",
    shapeName == "Jeollabuk-do" ~ "North Jeolla",
    shapeName == "Jeollanam-do" ~ "South Jeolla",
    shapeName == "Gyeongsangbuk-do" ~ "North Gyeongsang",
    shapeName == "Gyeongsangnam-do" ~ "South Gyeongsang",
    shapeName == "Jeju-do" ~ "Jeju",
    shapeName == "Gangwon-do" ~ "Gangwon",
    shapeName == "Gyeonggi-do" ~ "Gyeonggi",
    .default = shapeName
    )
  ) 

rok_fertility_shapefile_2022 <- 
  full_join(rok, rok_fertility_province_2022, by = join_by(shapeName)) |>
  st_as_sf(crs =  5178 )

rok_fertility_shapefile_metropolitan_2022 <-
  rok_fertility_shapefile_2022 |>
  filter(shapeName %in% c("Seoul", "Busan", "Daegu", "Incheon", "Gwuangju", "Daejeon", "Ulsan"))


# plot code

korea_fertility_plot_2022 <-
  ggplot() + 
  geom_sf(data = rok_fertility_shapefile_2022, aes(fill = fertility_rate)) +
  geom_sf_text(data = rok_fertility_shapefile_metropolitan_2022, mapping = aes(label = shapeName), label.size = 0.01, stat = "sf_coordinates", size = 2.5, color = "black", position = position_dodge()) +
  scale_fill_continuous(
    name = "Total Fertility Rate \n Number of Children",
    low = "#fff",
    high = "pink"
  ) +
  theme_void() +
   theme(text = element_text(face = "bold")) +
   labs(title = "South Korea's Fertility Rate",
       subtitle = "South Korea is below replacement rate(2.1 children) nationwide, \n especially in metropolitan areas",
       caption = "Source: Korean Statistical Information Service")

korea_fertility_plot_2022

ggsave(filename = "korea_5178_projection.pdf")

```

Beginning to make Korea GRDP plot

```{r}


rok_grdp_2022 <-
  read_excel("data/Korean GRDP Wikipedia Excel import.xlsx") |>
  clean_names() |>
  mutate(region = case_when(
    region == "Gangwon Province, South Korea" ~ "Gangwon",
    region == "Gyeonggi Province" ~ "Gyeonggi",
    region == "Jeju Province" ~ "Jeju",
    region == "North Chungcheong Province" ~ "North Chungcheong",
    region == "North Gyeongsang Province" ~ "North Gyeongsang",
    region == "North Jeolla Province" ~ "North Jeolla",
    region == "South Chungcheong Province" ~ "South Chungcheong",
    region == "South Gyeongsang Province" ~ "South Gyeongsang",
    region == "South Jeolla Province" ~ "South Jeolla",
    .default = region
  )
  ) |> 
  rename(shapeName = region)


# do gsub to get gdp data to numeric

rok_grdp_2022$gdp_won <- 
 as.numeric(gsub("KR₩|trillion", "", rok_grdp_2022$gdp_won))


rok_grdp_2022$gdp_us <-
  as.numeric(gsub("US\\$|billion","",rok_grdp_2022$gdp_us))


# Korean GRDP data source , cleaning data up

rok_gdp_shapefile_2022 <- 
  full_join(rok, rok_grdp_2022, by = join_by(shapeName)) |>
  st_as_sf(crs =  5178)

  

```

```{r}

korea_grdp_plot_2022 <-
  ggplot() + 
  geom_sf(data = rok_gdp_shapefile_2022, aes(fill = gdp_us)) +
  scale_fill_gradient(
    name = "Gross Domestic Regional Product (2022 $US)",
    low = "#fff",
    high = "#0F64CD",
    scales::dollar_format()
  ) + 
  theme_void() 

korea_grdp_plot_2022
```

```{r stich}
#| warning: false

korea_fertility_plot_2022 / korea_grdp_plot_2022

```


\pagebreak

## Graph 2 - Observing changes in South Korea's GDP and Fertility Rates over time: 1970 - 2023

Data Source: []() - remember to add to repo

```{r graph 2}
#| warning: false
#| message: false

# bringing in fertility data over time

rok_fertility_1970_2023 <-
  read_csv("data/Vital_Statistics_of_Korea_20241.csv",
           col_types = cols(`1970` = col_double(), 
                            `1971` = col_double(), 
                            `1972` = col_double(), 
                            `1973` = col_double(), 
                            `1974` = col_double(), 
                            `1975` = col_double(),
                            `1976` = col_double(),
                            `1977` = col_double(),
                            `1978` = col_double(),
                            `1979` = col_double(),
                            `1980` = col_double(),
                            `1981` = col_double(),
                            `1982` = col_double(),
                            `1983` = col_double(),
                            `1984` = col_double(),
                            `1985` = col_double(),
                            `1986` = col_double(),
                            `1987` = col_double(),
                            `1988` = col_double(),
                            `1989` = col_double(),
                            `1990` = col_double(),
                            `1991` = col_double(),
                            `1992` = col_double(),
                            `1993` = col_double(),
                            `1994` = col_double(),
                            `1995` = col_double(),
                            `1996` = col_double(),
                            `1997` = col_double(),
                            `1998` = col_double(),
                            `1999` = col_double(),
                            `2000` = col_double(),
                            `2001` = col_double(),
                            `2002` = col_double(),
                            `2003` = col_double(),
                            `2004` = col_double(),
                            `2005` = col_double(),
                            `2006` = col_double(),
                            `2007` = col_double(),
                            `2008` = col_double(),
                            `2009` = col_double(),
                            `2010` = col_double(),
                            `2011` = col_double(),
                            `2012` = col_double(),
                            `2013` = col_double(),
                            `2014` = col_double(),
                            `2015` = col_double(),
                            `2016` = col_double(),
                            `2017` = col_double(),
                            `2018` = col_double(),
                            `2019` = col_double(),
                            `2020` = col_double(),
                            `2021` = col_double(),
                            `2022` = col_double(),
                            `2023` = col_double())
           ) |>
  pivot_longer(
    cols = 2:55,
    names_to = "year") |>
  pivot_wider(
    names_from = "By items",
    values_from = value
  ) |>
  clean_names() |>
  select(year, total_fertility_rate_persons) 

rok_fertility_1970_2023$year <- as.numeric(rok_fertility_1970_2023$year)



# bringing in global gdp data , cleaning up

world_gdp_2023 <- 
  read_excel("data/gdp_2023.xls") |>
  clean_names() # from janitor() package 

world_gdp_2023 <- 
  world_gdp_2023 |>
  pivot_longer(
    cols = starts_with("x", ignore.case = TRUE),
    names_to = "year",
    values_to = "gdp",
    values_drop_na = TRUE
    ) |>
  select(-indicator_code)

world_gdp_2023$year <- as.numeric(gsub("x","",world_gdp_2023$year)) # prep for time series viz 

rok_gdp_1970_2023 <- 
  world_gdp_2023 |>
  filter(country_code == "KOR") |>
  mutate(gdp = gdp/10e6)

rok_gdp_fertility <-
  full_join(x = rok_fertility_1970_2023, y = rok_gdp_1970_2023, by = join_by(year))


# create south korea's fertility-gdp comparison map

ggplot(data = rok_gdp_fertility, aes(x = gdp, y = total_fertility_rate_persons, label = year)) +
  geom_point() +
  geom_text_repel(size = 3) + 
  geom_smooth(se = FALSE) +
  labs(
    title = "The Relationship between \nGross Domestic Product (GDP) & Fertility Rate in South Korea: 1970 - 2023",
    subtitle = str_wrap("Overtime, South Korea's GDP has increased while the Fertility Rate has decreased"),
    caption = "Source: The World Bank, Korean Statistical Information Service (KOSIS)",
    x = "GDP (US$ - 2023)",
    y = "Total Fertility Rate (Persons)") + 
  theme_minimal() + 
  theme(
    panel.grid = element_blank(),
    axis.line = element_line() 
  )


```

**MAKE SURE TO COMMIT AFTER FINSIHING**

\pagebreak

## Graph 3 -

Data Source: []() - remember to add to repo

```{r}


```

**MAKE SURE TO COMMIT AFTER FINSIHING**

## Graph 4 - 

Data Source: []() - remember to add to repo 

```{r}


```

**MAKE SURE TO COMMIT AFTER FINSIHING**

\pagebreak 
