---
title: "index"
author: "D'Angelo Francis; Su Yeon Seo"
format: html
---

```{r setup}
# make sure to load all packages here up top. If you need to install a package, include the commented code here as well :)

library(fontawesome) # install.packages("fontawesome") - for waffle graphs
library(styler) # install.packages("styler") - check for Tidy style guide adherence
library(lintr) # install.packages("lintr") - check for Tidy style guide adherence
```

## Quick Reference Links:

I believe that we will need these links 

- [Figures](https://quarto.org/docs/authoring/figures.html)
- [Cross Reference](https://quarto.org/docs/authoring/cross-references.html)
- [Tidyverse Style Guide Packages](https://style.tidyverse.org/)
- [Urban Style Visualization Style Guide](https://urbaninstitute.github.io/r-at-urban/graphics-guide.html)


## Graph 1 - 

Data Source: [Data.gov website](https://catalog.data.gov/dataset/) - remember to add actual data to repo

Highly interested in looking at this dataset more...

```{r graph 1}



```

**MAKE SURE TO COMMIT AFTER FINSIHING**

\pagebreak

## Graph 2 - 

Data Source: []() - remember to add to repo

```{r graph 2}


```

**MAKE SURE TO COMMIT AFTER FINSIHING**

\pagebreak

## Graph 3 -

Data Source: []() - remember to add to repo

```{r}


```

**MAKE SURE TO COMMIT AFTER FINSIHING**

## Graph 4 - 

Data Source: []() - remember to add to repo 

```{r}


```

**MAKE SURE TO COMMIT AFTER FINSIHING**

\pagebreak 
